---
title: "Writing Reports with R Markdown"
author: "Hector Mendoza"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include = FALSE}
library(tidyverse)
```

This report was prepared to the attention of the UN. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country's economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data, include = FALSE}
gapminder_1997 <- read_csv(file = 'Desktop/un-report/data/gapminder_1997.csv')
```
```{r gpd_lifeexp_1997, echo = FALSE}
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, color = continent, size = pop/1000000) +
  geom_point() +
  labs(x = "GDP per Capita", y = "Life Expectancy", title = 'Do people in wealthy countries live longer?', size = 'Population (in millions)')
```

```{r variables, include = FALSE}
nCountries <- gapminder_1997 %>% 
  select(country) %>% 
  n_distinct()

minGDP <- gapminder_1997 %>% 
  summarise(round(min(gdpPercap))) %>% 
  pull()

maxGDP <- gapminder_1997 %>% 
  summarise(round(max(gdpPercap))) %>% 
  pull()
```

The above plot shows the relationship between GDP per capita and life expectancy for a total of `r nCountries` countries. For this set of countries, economic wealth ranged from a minimum of USD `r minGDP` to a maximum of USD `r maxGDP` per capita.

|HEADER 1|HEADER 2|
|--------|--------|
|row 1, column 1|row 1, column 2|
|row 2, column 2|row 2, column 2|

|Summary of Data|
|---------------|
|Nujmber of Countries|`r nCountries`|
|Minimum GDP per capita|`r minGDP`|
|Maximum GDP per capita|`r maxGDP`|

```{r kabletable, echo = FALSE}
library(knitr)

gapminder_1997 %>% 
  filter(continent == 'Oceania') %>% 
  kable()
```

# Header 1
## Header 2
### My third header

#### Exercise

My list:

1. **R**
2. *kable()*
3. ***NGS Analysis***
4. [Basic Syntax Cheat Sheet](https://www.markdownguide.org/cheat-sheet/)
